Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors

### 2012-12-15 Publications/2013-IPMI/Latex/00-Main.tex
fixing affiliations and merge

\title{Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors}
%%
\titlerunning{Simultaneous segmentation and distortion correction on DWI}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Oscar Esteban\inst{1,2} \and
        Alessandro Daducci \inst{2} \and
		Meritxell Bach-Cuadra \inst{2,3} \and
		Mar\'ia-Jes\'us Ledesma-Carbayo \inst{1} \and 
        Jean-Philippe Thiran \inst{2,3} \and
        Andr\'es Santos \inst{1} \and
        Dominique Zosso \inst{2,4}}
%
\authorrunning{Oscar Esteban et al.} % abbreviated author list (for running head)

>>>>

\title{Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors}
%%
\titlerunning{Simultaneous segmentation and distortion correction on DWI}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Oscar Esteban\inst{1,2} \and
        Alessandro Daducci \inst{2} \and
		Meritxell Bach-Cuadra \inst{2,3} \and
        Jean-Philippe Thiran \inst{2,3} \and
        Andr\'es Santos \inst{1} \and
        Dominique Zosso \inst{2,4}}
%
\authorrunning{Oscar Esteban et al.} % abbreviated author list (for running head)
